14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-20 rules/rules19.tex
Rules: Add draft watermark.
Rules: Fix typos.

  \item {\bf Experimental Strings Division.}
    The competition will feature an experimental divisions for benchmarks that
    use strings. Participating solvers must implement the semantics of the
    current SMT-LIB draft for the theory of unicode strings
    (\url{http://smtlib.cs.uiowa.edu/theories-UnicodeStrings.shtml}).
    \rationale{Corresponding theories and benchmarks are expected to be added
    to SMT-LIB in the near future.}

@@

SMT-COMP 2019 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item
		Liana Hadarean~-- Amazon, USA (co-organizer)
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
		Universita della Svizzera italiana, Switzerland (co-organizer)
\item
  \href{http://cs.stanford.edu/people/niemetz}{Aina
    Niemetz}~-- Stanford University, USA (co-chair)
\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
  University of Manchester, UK (co-chair)
\end{itemize}
%
The competition charis are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

>>>>

  \item {\bf Experimental Strings Division.}
    The competition will feature experimental divisions for benchmarks that
    use strings. Participating solvers must implement the semantics of the
    current SMT-LIB draft for the theory of unicode strings
    (\url{http://smtlib.cs.uiowa.edu/theories-UnicodeStrings.shtml}).
    \rationale{Corresponding theories and benchmarks are expected to be added
    to SMT-LIB in the near future.}

@@

SMT-COMP 2019 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item
		Liana Hadarean~-- Amazon, USA (co-organizer)
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyvarinen}~--
		Universita della Svizzera italiana, Switzerland (co-organizer)
\item
  \href{http://cs.stanford.edu/people/niemetz}{Aina
    Niemetz}~-- Stanford University, USA (co-chair)
\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
  University of Manchester, UK (co-chair)
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.
